\documentclass[12pt]{article}

%\usepackage[T1]{fontenc}
%\usepackage{mathpazo}
\usepackage{fullpage}
\usepackage{amsmath,amsfonts}
\usepackage{textgreek}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Bembo Book MT Pro}
%\setromanfont[Mapping=tex-text]{Minion Pro}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Remove paragraph indentation
\usepackage[parfill]{parskip}

% Fixes for letterspacing that work with XeLaTeX
\newcommand{\allcapsspacing}[1]{{\addfontfeature{LetterSpace=7.5}#1}}
\newcommand{\smallcapsspacing}[1]{{\addfontfeature{LetterSpace=5.0}#1}}
\renewcommand{\textsc}[1]{\smallcapsspacing{\scshape{#1}}}

\usepackage{CV}
%\usepackage[letterspace=100]{microtype}

\newcommand{\tworowstwocolsitem}[4]{
{#1} \hfill {#2} \\
{#3} \hfill {#4} \\
\vspace{-0.5\baselineskip}\par}

\newcommand{\educationitem}[4]{
\tworowstwocolsitem{\textbf{#1}}{#2}{\textit{#3}}{\textit{#4}}}

\newcommand{\teachingitem}[4]{
\tworowstwocolsitem{#1}{#2}{\textit{#3}}{#4}}

\newcommand{\leadershipitem}[3]{
\textbf{#1} \hfill {#2} \\
#3 \\
\vspace{-0.5\baselineskip}\par}

\newcommand{\outreachitem}[4]{
{#1} \hfill {#2} \\
#3 \par
#4 
\par\vspace{0.5\baselineskip}}

\newcommand{\researchitem}[4]{
\outreachitem{#1}{#2}{\textit{#3}}{\vspace{0.5\baselineskip}#4}}

\newcommand{\yearitem}[2]{
{#1} \hfill {#2} \\
\vspace{-0.5\baselineskip}\par}

\usepackage{titlesec}
\titleformat{\section}{}{}{}{\hrule\vspace{0.5\baselineskip}\sffamily\large\uppercase}{}{}
\titlespacing{\section}{0pt}{-15pt}{*1}

\titleformat{\subsection}{}{}{}{\sffamily\normalsize\uppercase}{}{}

% enables reverse numbering
\usepackage[leftmargin=12pt, itemsep=0.5\baselineskip]{etaremune}

\usepackage{xcolor}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % clears the header and footer
\renewcommand{\headrulewidth}{0pt} % removes the horizontal line that comes with fancyhdr
\rfoot{\color{gray}\thepage}
\lfoot{\color{gray}Weitzner}

\begin{document}

\begin{center}
\Large{\sffamily\allcapsspacing{\uppercase{Brian D. Weitzner}, Ph.D.}}

\normalsize{\textsc{Department of Chemical \& Biomolecular Engineering \\
Johns Hopkins University \\
3400 N. Charles Street, Baltimore, Maryland 21218 \\
\vspace{0.25\baselineskip}
brian.weitzner@jhu.edu \hspace{12pt} phone:} 856.316.8337}
\end{center}

\section*{\allcapsspacing{Education}}
\educationitem{The Johns Hopkins University}{Baltimore, MD}{Ph.D. Chemical \& Biomolecular Engineering}{March 2015}
\vspace{-\baselineskip}
Dissertation title: Next-generation antibody modeling.

\educationitem{Cornell University}{Ithaca, NY}{B.S. Chemical \& Biomolecular Engineering, Minor Biomedical Engineering, Cum Laude}{May 2009}

\section*{\allcapsspacing{Research Experience}}
\researchitem{\textbf{Postdoctoral Fellow}, The Johns Hopkins University}{March 2015--Present}{Advisor: Dr. Jeffrey J. Gray}{
Developed a new method for \textit{de novo} CDR H3 loop structure prediction using structure-based constraints.
% Redesigned and implemented an all-new codebase for RosettaAntibody.
}

\researchitem{\textbf{Graduate Research Assistant}, The Johns Hopkins University}{August 2009--March 2015}{Advisor: Dr. Jeffrey J. Gray}{
My studies focused on antibody structure prediction, namely accurate \textit{de novo} modeling of the CDR H3 loop.
I determined the weaknesses in existing structure prediction methods during a blind structure prediction challenge.
To rectify these weaknesses, I performed statistical analyses of known structures of antibodies and non-antibody proteins to determine what governs the conformation of CDR H3 loops.
Using the results from these analyses, I formulated a structure-based constraint that can be applied during \textit{de novo} modeling to produce accurate models of CDR H3 loops.
During this work I developed a new hypothesis regarding the functional utility of the C-terminal kink present in most antibody CDR H3 loops.}

\researchitem{\textbf{Undergraduate Research Assistant}, Cornell University}{November 2006--May 2009}{Advisors: Dr. Matthew P. DeLisa \& Dr. Jeffrey D. Varner}{
I began a collaborative project between the DeLisa and Varner research groups with the aim of computationally retargeting an E3 ubiquitin ligase.
I performed \textit{in silico} mutational and protein--protein docking studies.
Loss of function predictions were successful, however full retargeting remains an open problem.}

\researchitem{\textbf{Undergraduate Research Assistant}, Fox Chase Cancer Center}{June 2005--August 2009}{Advisor: Dr. Roland L. Dunbrack, Jr.}{
I studied dimerization motifs of cytosolic sulfotransferases by analyzing the unique interfaces in every available sulfotransferase crystal structure.
I identified a small interface that had previously been shown to be biologically significant in every crystal structure, indicating the functional quaternary structure was contained in each crystal structure.}

\researchitem{\textbf{Howard Hughes Student Scientist}, Fox Chase Cancer Center}{September 2004--June 2005}{Advisor: Dr. Roland L. Dunbrack, Jr.}{
As a high school student, I studied the agreement among quaternary structure assignments, namely the Protein Data Bank (PDB) and the Protein Quaternary Structure (PQS) server.
The analysis showed that, at the time, neither server should be considered definitive, and instead both should be used.}

\section*{\allcapsspacing{Publications}}
\begin{etaremune}
\item Porter JR, \textbf{Weitzner BD}, Lange OF (2015) ``A framework simplifying combined sampling modes in Rosetta,'' \textit{under review}
\item Alford RF*, Koehler Leman J*, \textbf{Weitzner BD}, Duran AM, Tilley DC, Elazar A, Gray JJ (2015) ``An integrated framework advancing membrane protein modeling and design,'' \textit{PLoS Comput. Biol.} In press. (* equal contribution authors)
\item \textbf{Weitzner BD}, Dunbrack RL, Jr, Gray JJ (2015) ``The origin of CDR H3 structural diversity,'' \textit{Structure}, 23(2), 302--11.
\item \textbf{Weitzner BD*}, Kuroda D*, Marze N, Xu J, Gray JJ (2014) ``Blind prediction performance of RosettaAntibody 3.0: Grafting, relaxation, kinematic loop modeling, and full CDR optimization,'' \textit{Proteins} 82(8), 1611--23. (* equal contribution authors)
\item Lyskov S, Chou F-C, Conch{\'u}ir S{\'O}, Der BS, Drew K, Kuroda D, Xu J, \textbf{Weitzner BD}, Renfrew PD, Sripakdeevong P, Borgo B, Havranek JJ, Kuhlman B, Kortemme T, Bonneau R, Gray JJ, Das R (2013) ``Serverification of Molecular Modeling Applications: The Rosetta Online Server That Includes Everyone (ROSIE),'' \textit{PLOS ONE} 8(5): e63906.
\item Baugh EH, Lyskov S, \textbf{Weitzner BD}, Gray JJ (2011) ``Real-time PyMOL visualization for Rosetta and PyRosetta,'' \textit{PLOS ONE} 6(8): e21931.
\item Chaudhury S, Berrondo M, \textbf{Weitzner BD}, Muthu P, Bergman H, Gray JJ (2011) ``Benchmarking and analysis of protein docking performance in Rosetta v3.2,'' \textit{PLOS ONE} 6(8): e22477.
\item Bourne PE, Beran B, Bi C, Bluhm W, Dunbrack R, Prlic A, Quinn G, Rose P, Shah R, Tao W, \textbf{Weitzner B}, Yukich, B (2010) ``Will Widgets and Semantic Tagging Change Computational Biology?'' \textit{PLoS Comput. Biol.} 6(2): e1000673.
\item \textbf{Weitzner B}, Meehan T, Xu Q, Dunbrack R (2009) ``An unusually small dimer interface is observed in all available crystal structures of cytosolic sulfotransferases,'' \textit{Proteins.} 75(2), 1097--134.
\end{etaremune}

\section*{\allcapsspacing{Funding}}
Contributed to and secured \textbf{NIH 5R01-GM078221}, ``Prediction of the structure of therapeutic antibodies with their antigens,'' 9/1/2012--8/31/2016, \$1,241,054 (\$821,600 direct).
Specifically responsible for the development of Aim 1: Improve prediction of long, hypervariable CDR H3 loops. \\ \vspace{-0.5\baselineskip}

Work toward this aim led to two first-author publications: (1) ``The origin of CDR H3 struct\-ur\-al diversity'' with RLD, and JJG; and (2) ``Blind prediction performance of Rosetta\-Antibody 3.0: Grafting, relaxation, kinematic loop modeling, and full CDR optimization'' with DK, NM, JX, and JJG.\\ \vspace{-0.5\baselineskip}

\section*{\allcapsspacing{Selected Honors and Awards}}
\yearitem{RosettaCon XIII Best Poster Award}{2015}
\yearitem{JHU ChemBE Department Graduate Student Award}{2015}
\yearitem{Rosetta Service Award: Instructor at inaugural Rosetta Boot Camp}{2013}
\yearitem{Rosetta Service Award: Leader of transition of Rosetta source\\code to a new version control system}{2013}
\yearitem{American Institute of Chemists Student Award}{2009}
\yearitem{1$^\text{st}$ place in national AIChE Car Competition;\\first team to ever perform perfectly}{2008}
\yearitem{Howard Hughes Medical Institute Student Scientist Program;\\Fox Chase Cancer Center}{2004--2005}
\yearitem{Eagle Scout}{2003}

\section*{\allcapsspacing{Invited Seminars and Talks}}
\begin{etaremune}
\item \textbf{Weitzner BD}, Gray JJ (2015) ``Next-generation Antibody Modeling'' \textit{Seminar, Institute for Cellular and Molecular Biology, University of Texas at Austin}, Austin, TX.
\item \textbf{Weitzner BD}, Gray JJ (2014) ``Next-generation Antibody Modeling'' \textit{Seminar, Center for Biomolecular Structure and Dynamics, University of Montana}, Missoula, MT.
\item \textbf{Weitzner BD}, Dunbrack RL, Gray JJ (2014) ``The origin of CDR H3 Structural Diversity'' \textit{Vor\-trag, Fakult\"{a}t f\"{u}r Chemie, Technische Universit\"{a}t M\"{u}nchen}, Munich, Germany.
\item \textbf{Weitzner BD}, Gray JJ (2013) ``Computational Structure Prediction, Docking and Design of Antibodies'' \textit{IBC Antibody Engineering and Therapeutics}, Huntington Beach, CA. (delivered on behalf of JJG during his paternity leave)
\end{etaremune}

\section*{\allcapsspacing{Conference Contributions}}
\subsection*{\allcapsspacing{Talks}}
\begin{etaremune}
\item \textbf{Weitzner BD}, Gray JJ (2015) ``Producing physically realistic structural models with RosettaAntibody'' \textit{America's Antibody Congress}, San Diego, CA.
\item \textbf{Weitzner BD}, Kuroda D, Marze N, Xu J, Gray JJ (2013) ``Benchmarking RosettaAntibody: Antibody Modeling Assessment II'' \textit{Antibody Engineering and Therapeutics Conference}, Huntington Beach, CA.
\item \textbf{Weitzner BD}, Roland RL, Gray JJ (2013) ``Kinked CDR H3-like loops are common'' \textit{AIChE Annual Conference}, San Francisco, CA
\item \textbf{Weitzner BD}, Dunbrack RL, Gray JJ (2013) ``Antibodies are proteins too!'' \textit{Rosetta Conference}, Leavenworth, WA.
\item \textbf{Lyskov S}, \textbf{Weitzner BD}, Gray JJ (2011) ``PyRosetta 2.0: I can make a new score term in 6 lines!'' \textit{Rosetta Conference}, Leavenworth, WA.
\item \textbf{Weitzner BD}, Leaver-Fay A, Kulp D,  Lyskov S (2010) ``Using PyRosetta for research'' \textit{Rosetta Conference}, Leavenworth, WA. [workshop]
\item \textbf{Weitzner BD}, Baugh EH, Gray JJ (2010) ``PyMOL--PyRosetta Integration'' \textit{Rosetta Conference}, Leavenworth, WA.
\end{etaremune}

\subsection*{\allcapsspacing{Posters}}
\begin{etaremune}
\item Weitzner, BD, Dunbrack RL, Gray JJ (2015) ``\textit{De novo} CDR-H3 loop structure prediction using a structurally derived kink constraint'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2015) ``The origin of CDR H3 Structural Diversity'' \textit{Biophysical Society Meeting}, Baltimore, MD.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2014) ``CDR H3 loop prediction'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2012) ``Are CDR H3 loops special?'' \textit{Rosetta Conference}, Leavenworth, WA.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2011) ``Accessing the conformation space of long CDR H3 loops through \textbeta-turn detection'' \textit{Rosetta Conference}, Leavenworth, WA.
\end{etaremune}

\section*{\allcapsspacing{Teaching Experience}}
\teachingitem{\textbf{Guest Lecturer}, ChemBE 414/614}{Fall 2014}{Computational Protein Structure Prediction and Design}{Johns Hopkins University}
This course is aimed at introducing the fundamental concepts in protein structure, biophysics, optimization and informatics that have enabled the breakthroughs in computational structure prediction and design to advanced seniors and interested graduate students.
My role in this course was delivering a lecture on side-chain conformations, optimization and libraries.
All course lectures are available on YouTube.\par\vspace{\baselineskip}

\teachingitem{\textbf{Co-Instructor}, Rosetta Boot Camp}{Spring 2013}{An intense week-long crash course to developing in Rosetta}{Chapel Hill, NC}
This course is aimed at introducing the computer science concepts and architecture of Rosetta to graduate students and postdocs who have just joined labs that develop Rosetta.
After this week-long course, students should be able to use Rosetta to solve specific structure prediction and design problems as well as develop new methods tailored to a specific problem.
I delivered three lectures and guided lab sessions.
All course lectures are available on YouTube.\par\vspace{\baselineskip}

\teachingitem{\textbf{Co-Instructor}, ChemBE 418}{Fall 2011}{Projects in the Design of a Chemical Car}{Johns Hopkins University}
Undergraduate students work in small groups over the course of the semester to design and build a chemically powered vehicle that will compete with other college teams at the American Institute of Chemical Engineers (AIChE) Regional Conference. 
The students must design and construct the chassis as well as chemically powered propulsion and break mechanisms within the constraints of the competition. In addition, students will give oral presentation, write reports, and do thorough safety analysis of their prototypes.
My role as a co-instructor was to challenge the students' designs, assist them in organizing their experiments and keeping on schedule to successfully construct their car.\par\vspace{\baselineskip}

\teachingitem{\textbf{Teaching Assistant}, ChemBE 409}{Fall 2010}{Modeling, Dynamics \& Control of Chemical \& Biological Systems}{Johns Hopkins University}
This course introduces the modeling, dynamics, and control concepts necessary for the unsteady state analysis of biomolecular and chemical processes to seniors in the Chemical \& Biomolecular Engineering program.
Model construction for biomolecular and cellular systems including pharmacokinetic modeling, biomolecular modeling using the central dogma of biology/control of gene expression, large scale biosimulation.
I held office hours, proctored exams, ran a lab assignment and assisted students with model analysis using Matlab.\par\vspace{\baselineskip}

\teachingitem{\textbf{Teaching Assistant}, ChemBE 414/614}{Spring 2010}{Computational Protein Structure Prediction and Design}{Johns Hopkins University}
This course is aimed at introducing the fundamental concepts in protein structure, biophysics, optimization and informatics that have enabled the breakthroughs in computational structure prediction and design to advanced seniors and interested graduate students.
My role in this course was running the weekly laboratory sessions as well as grading homework assignments.\par\vspace{\baselineskip}

\teachingitem{\textbf{Teaching Assistant}, ChemE 3900}{Spring 2009}{Chemical Kinetics and Reactor Design}{Cornell University}
This course is aimed at junior-level undergraduates to introduce the study of chemical reaction kinetics and principles of reactor design for chemical processes.
The students develop a molecular-level understanding of chemical reaction kinetics, practical approaches to modeling complex reactions, and the ability to construct mathematical models to predict system behavior from first principles.
With these tools in hand, the students learn to optimize reactor design with regard to multiple performance criteria.
My role in this course was presenting problems along with solutions in weekly recitation sessions.\par\vspace{\baselineskip}

\teachingitem{\textbf{Teaching Assistant}, ChemE 1120}{Fall 2008}{Introduction to Chemical Engineering}{Cornell University}
This course introduces freshman undergraduate students to design strategies for contemporary chemical and biomolecular engineering.
Methods for analyzing designs, mathematical modeling, empirical analysis by graphics, and dynamic scaling through dimensional analysis are also covered in the context of assessing product quality, economics, safety, and environmental issues.
My role in this course was grading assignments and presenting problems along with solutions in weekly recitation sessions.\par\vspace{\baselineskip}

\section*{\allcapsspacing{Scientific Leadership}}
\leadershipitem{Developed RosettaCon Code of Conduct}{2014}{Led the development and implementation of Code of Conduct for RosettaCon to promote diversity. Served on the incident reporting panel 2014--2015.}
\leadershipitem{Rosetta Boot Camp, Course Co-director}{2013}{Identified need for training graduate students and postdocs. Helped developed curriculum to introduce students to Rosetta.}
\leadershipitem{Undergraduate research mentor}{2012--2014}{Mentor to four undergraduate researchers in the Gray Lab}
\leadershipitem{Organizer, Rosetta Developer Meeting}{2012}{Arranged the program, travel, lodging and meals}

\section*{\allcapsspacing{Activities and Outreach}}
\leadershipitem{Student volunteer, STEM Achievement in Baltimore Elementary Schools}{2013--2015}{Monthly visits to a Baltimore City elementary school to facilitate learning STEM skills}
\leadershipitem{Runner, Baltimore Marathon}{2012}{\vspace{-\baselineskip}}
\leadershipitem{Member of the Extreme Rosetta Workshop (XRW) Team}{2010--2011}{A small team of developers gathered to overhaul the structure of the Rosetta source code}
\leadershipitem{Volunteer at the Ricky Myers Day of Service}{Fall 2010}{A city-wide day of service to clean parks, plant gardens, repair homes and more}
\leadershipitem{Member of the JHU ChemBE Department STEM outreach group}{2009--2013}{Visits to a Baltimore Recreation Center to teach children about STEM through demonstrations and activities}
\leadershipitem{Captain of the AIChE Car Team, Cornell University}{2008--2009}{Leader of the team, organized various sub-groups and kept the project on schedule}
\leadershipitem{Member of the AIChE Car Team, Cornell University}{2006--2008}{A project team that builds a shoe box-sized car that is powered and stopped by chemical reactions}

\end{document}
