\documentclass[11pt]{article}

%\usepackage[T1]{fontenc}
%\usepackage{mathpazo}
\usepackage{fullpage}
%\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath,amsfonts}
\usepackage{textgreek}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Bembo Book MT Pro}
%\setromanfont[Mapping=tex-text]{Minion Pro}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

% Remove paragraph indentation
\usepackage[parfill]{parskip}

%% Fixes for letterspacing that work with XeLaTeX
\newcommand{\allcapsspacing}[1]{{\addfontfeature{LetterSpace=7.5}#1}}
\newcommand{\smallcapsspacing}[1]{{\addfontfeature{LetterSpace=5.0}#1}}
\renewcommand{\textsc}[1]{\smallcapsspacing{\scshape{#1}}}

\usepackage{CV}
%\usepackage[letterspace=100]{microtype}

\newcommand{\tworowstwocolsitem}[4]{
{#1} \hfill {#2} \\
{#3} \hfill {#4} \\
\vspace{-0.5\baselineskip}\par}

\newcommand{\educationitem}[4]{
\tworowstwocolsitem{\textbf{#1}}{#2}{\textit{#3}}{\textit{#4}}}

\newcommand{\teachingitem}[4]{
\tworowstwocolsitem{#1}{#2}{\textit{#3}}{#4}}

\newcommand{\leadershipitem}[3]{
\textbf{#1} \hfill {#2} \\
#3 \\
\vspace{-0.5\baselineskip}\par}

\newcommand{\outreachitem}[4]{
{#1} \hfill {#2} \\
#3 \par
#4 
\par\vspace{0.5\baselineskip}}

\newcommand{\researchitem}[4]{
\outreachitem{#1}{#2}{\textit{#3}}{\vspace{0.5\baselineskip}#4}}

\newcommand{\yearitem}[2]{
{#1} \hfill {#2} \\
\vspace{-0.5\baselineskip}\par}

\usepackage{titlesec}
\titleformat{\section}{}{}{}{\vspace{0.25\baselineskip}\hrule\sffamily\large\uppercase}{}{}
\titlespacing{\section}{0pt}{-18pt}{*1}

\titleformat{\subsection}{}{}{}{\sffamily\normalsize\uppercase}{}{}
\titlespacing{\subsection}{0pt}{0pt}{*1}

% enables reverse numbering
\usepackage[leftmargin=12pt, itemsep=0.25\baselineskip]{etaremune}

%\pagestyle{empty}

\usepackage{xcolor}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % clears the header and footer
\renewcommand{\headrulewidth}{0pt} % removes the horizontal line that comes with fancyhdr
\rfoot{\color{gray}\thepage}
\lfoot{\color{gray}Weitzner}

\begin{document}

\begin{center}
\large{\sffamily\allcapsspacing{\uppercase{Brian D. Weitzner}, Ph.D.}}

\normalsize{\textsc{Department of Chemical \& Biomolecular Engineering,
Johns Hopkins University \\
3400 N. Charles Street, Baltimore, Maryland 21218 \\
%\vspace{0.25\baselineskip}
brian.weitzner@jhu.edu \hspace{12pt} phone:} 856.316.8337}
\end{center}

\section*{\allcapsspacing{Education}}
\educationitem{The Johns Hopkins University}{Baltimore, MD}{Ph.D. Chemical \& Biomolecular Engineering}{March 2015}
\vspace{-\baselineskip}
Dissertation title: Next-generation antibody modeling.

\educationitem{Cornell University}{Ithaca, NY}{B.S. Chemical \& Biomolecular Engineering, Minor Biomedical Engineering}{May 2009}

\section*{\allcapsspacing{Research Experience}}
\researchitem{\textbf{Graduate Research Assistant/Postdoctoral Fellow}, The Johns Hopkins University}{2009--2015}{Advisor: Dr. Jeffrey J. Gray}{\vspace{-0.75\baselineskip}}
\researchitem{\textbf{Undergraduate Research Assistant}, Cornell University}{2006--2009}{Advisors: Dr. Matthew P. DeLisa \& Dr. Jeffrey D. Varner}{\vspace{-0.75\baselineskip}}
\researchitem{\textbf{Undergraduate Research Assistant}, Fox Chase Cancer Center}{2005--2009}{Advisor: Dr. Roland L. Dunbrack, Jr.}{\vspace{-0.75\baselineskip}}
\researchitem{\textbf{Howard Hughes Student Scientist}, Fox Chase Cancer Center}{2004--2005}{Advisor: Dr. Roland L. Dunbrack, Jr.}{\vspace{-0.75\baselineskip}}

\section*{\allcapsspacing{Publications}}
\begin{etaremune}
\item Porter JR, \textbf{Weitzner BD}, Lange OF (2015) ``A framework simplifying combined sampling modes in Rosetta,'' \textit{under review}
\item Alford RF*, Koehler Leman J*, \textbf{Weitzner BD}, Duran AM, Tilley DC, Elazar A, Gray JJ (2015) ``An integrated framework advancing membrane protein modeling and design,'' \textit{PLoS Comput. Biol.} In press. (* equal contribution authors)
\item \textbf{Weitzner BD}, Dunbrack RL, Jr, Gray JJ (2014) ``The origin of CDR H3 structural diversity,'' \textit{Structure}, accepted.
\item \textbf{Weitzner BD*}, Kuroda D*, Marze N, Xu J, Gray JJ (2014) ``Blind prediction performance of RosettaAntibody 3.0: Grafting, relaxation, kinematic loop modeling, and full CDR optimization,'' \textit{Proteins} 82(8), 1611-23. (* equal contribution authors)
\item Lyskov S, Chou F-C, Conch{\'u}ir S{\'O}, Der BS, Drew K, Kuroda D, Xu J, \textbf{Weitzner BD}, Renfrew PD, Sripakdeevong P, Borgo B, Havranek JJ, Kuhlman B, Kortemme T, Bonneau R, Gray JJ, Das R (2013) ``Serverification of Molecular Modeling Applications: The Rosetta Online Server That Includes Everyone (ROSIE),'' \textit{PLOS ONE} 8(5): e63906.
\item Baugh EH, Lyskov S, \textbf{Weitzner BD}, Gray JJ (2011) ``Real-time PyMOL visualization for Rosetta and PyRosetta,'' \textit{PLOS ONE} 6(8): e21931.
\item Chaudhury S, Berrondo M, \textbf{Weitzner BD}, Muthu P, Bergman H, Gray JJ (2011) ``Benchmarking and analysis of protein docking performance in Rosetta v3.2,'' \textit{PLOS ONE} 6(8): e22477.
\item Bourne PE, Beran B, Bi C, Bluhm W, Dunbrack R, Prlic A, Quinn G, Rose P, Shah R, Tao W, \textbf{Weitzner B}, Yukich, B (2010) ``Will Widgets and Semantic Tagging Change Computational Biology?'' \textit{PLoS Comput. Biol.} 6(2): e1000673.
\item \textbf{Weitzner B}, Meehan T, Xu Q, Dunbrack R (2009) ``An unusually small dimer interface is observed in all available crystal structures of cytosolic sulfotransferases,'' \textit{Proteins.} 75(2), 1097-134.
\end{etaremune}

\section*{\allcapsspacing{Teaching Experience}}
\yearitem{\textbf{Guest Lecturer, ChemBE 414/614}: \textit{Computational Protein Structure Prediction and Design}}{JHU, Fall 2014}
\yearitem{\textbf{Co-Instructor}, Rosetta Boot Camp: \textit{An intense crash course to developing in Rosetta}}{UNC, Spring 2013}
\yearitem{\textbf{Co-Instructor}, ChemBE 418: \textit{Projects in the Design of a Chemical Car}}{JHU, Fall 2011}
\yearitem{\textbf{Teaching Assistant}, ChemBE 409: \textit{Modeling, Dynamics \& Control of Chemical \& Biological Systems}}{JHU, Fall 2010}
\yearitem{\textbf{Teaching Assistant}, ChemBE 414/614: \textit{Computational Protein Structure Prediction and Design}}{JHU, Spring 2010}
\yearitem{\textbf{Teaching Assistant}, ChemE 3900: \textit{Chemical Kinetics and Reactor Design}}{Cornell University, Spring 2009}
\yearitem{\textbf{Teaching Assistant}, ChemE 1120: \textit{Introduction to Chemical Engineering}}{Cornell University, Fall 2008}

\section*{\allcapsspacing{Scientific Leadership}}
\leadershipitem{Developed RosettaCon Code of Conduct}{2014}{Led the development and implementation of Code of Conduct for RosettaCon to promote diversity. Served on the incident reporting panel 2014--2015.}
\leadershipitem{Rosetta Boot Camp}{2013}{Identified need for training graduate students and postdocs. Helped developed curriculum to introduce students to Rosetta.}
\leadershipitem{Undergraduate research mentor}{2012--2014}{Mentor to four undergraduate researchers in the Gray Lab}
\leadershipitem{Organizer, Rosetta Developer Meeting}{2012}{Arranged the program, travel, lodging and meals}

\section*{\allcapsspacing{Invited Seminars and Talks}}
\begin{etaremune}
\item Weitzner BD, Gray JJ (2015) ``Next-generation Antibody Modeling'' \textit{Seminar, Institute for Cellular and Molecular Biology, University of Texas at Austin}, Austin, TX.
\item Weitzner BD, Gray JJ (2014) ``Next-generation Antibody Modeling'' \textit{Seminar, Center for Biomolecular Structure and Dynamics, University of Montana}, Missoula, MT.
\item Weitzner BD, Dunbrack RL, Gray JJ (2014) ``The origin of CDR H3 Structural Diversity'' \textit{Vortrag, Fakult\"{a}t f\"{u}r Chemie, Technische Universit\"{a}t M\"{u}nchen}, Munich, Germany.
\item Weitzner BD, Gray JJ (2013) ``Computational Structure Prediction, Docking and Design of Antibodies'' \textit{IBC Antibody Engineering and Therapeutics}, Huntington Beach, CA. (delivered on behalf of JJG during his paternity leave)
\end{etaremune}

\section*{\allcapsspacing{Conference Contributions}}
\subsection*{\allcapsspacing{Talks}}
\begin{etaremune}
\item \textbf{Weitzner BD}, Gray JJ (2015) ``Producing physically realistic structural models with RosettaAntibody'' \textit{America's Antibody Congress}, San Diego, CA.
\item \textbf{Weitzner BD}, Kuroda D, Marze N, Xu J, Gray JJ (2013) ``Benchmarking RosettaAntibody: Antibody Modeling Assessment II'' \textit{Antibody Engineering and Therapeutics Conference}, Huntington Beach, CA.
\item \textbf{Weitzner BD}, Roland RL, Gray JJ (2013) ``Kinked CDR H3-like loops are common'' \textit{AIChE Annual Conference}, San Francisco, CA
\item \textbf{Weitzner BD}, Dunbrack RL, Gray JJ (2013) ``Antibodies are proteins too!'' \textit{RosettaCon}, Leavenworth, WA.
\item \textbf{Lyskov S}, \textbf{Weitzner BD}, Gray JJ (2011) ``PyRosetta 2.0: I can make a new score term in 6 lines!'' \textit{RosettaCon}, Leavenworth, WA.
\item \textbf{Weitzner BD}, Leaver-Fay A, Kulp D,  Lyskov S (2010) ``Using PyRosetta for research'' \textit{RosettaCon}, Leavenworth, WA. [workshop]
\item \textbf{Weitzner BD}, Baugh EH, Gray JJ (2010) ``PyMOL--PyRosetta Integration'' \textit{RosettaCon}, Leavenworth, WA.
\end{etaremune}

\subsection*{\allcapsspacing{Posters}}
\begin{etaremune}
\item Weitzner, BD, Dunbrack RL, Gray JJ (2015) ``\textit{De novo} CDR-H3 loop structure prediction using a structurally derived kink constraint'' \textit{RosettaCon}, Leavenworth, WA.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2015) ``The origin of CDR H3 Structural Diversity'' \textit{Biophys. Soc. Mtg.}, Baltimore, MD.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2014) ``CDR H3 loop prediction'' \textit{RosettaCon}, Leavenworth, WA.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2012) ``Are CDR H3 loops special?'' \textit{RosettaCon}, Leavenworth, WA.
\item Weitzner, BD, Dunbrack RL, Gray JJ (2011) ``Accessing the conformation space of long CDR H3 loops through \textbeta-turn detection'' \textit{RosettaCon}, Leavenworth, WA.
\end{etaremune}
\end{document}
